Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2021-10-25 Presentations/ThirdYearPaperpres.tex
Updates from Overleaf

Did EHR implementation in hospitals affect labor market decisions of physicians, specifically where, and how much they work?

@@

\begin{frame}{Effect of Health Information Technology}

@@

\begin{frame}{Physician Labor Decisions}

@@

\begin{frame}[shrink=30]{Total Patients}
\centering
\import{Objects/}{continuous.tex}
\end{frame}

\begin{frame}[shrink=30]{Total Patients}
\centering
\import{Objects/}{continuous_old.tex}
\end{frame}

\begin{frame}[shrink=30]{Working}
\centering
\import{Objects/}{indicator.tex}
\end{frame}

\begin{frame}[shrink=30]{Retirement?}
\centering
\import{Objects/}{indicator_old.tex}
\end{frame}

>>>>

Did EHR implementation in hospitals affect physician labor outcomes?
\begin{itemize}
    \item Intensive Margin
    \item Extensive Margin
    \item Hospital $\rightarrow$ Office?
\end{itemize}

@@

\begin{frame}{Health Information Technology}

@@

\begin{frame}{Physician Labor}

\begin{frame}{Technology and Labor Relationship}

@@

\begin{frame}{Full Sample Event Study}
\centering
\includegraphics[scale=.7]{Objects/event_hosp_fullsample.pdf}
